---
title: "Quiz 1"
author: "Jake"
date: "December 9, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here:
https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv
and load the data into R. The code book, describing the variable names is here:
https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FPUMSDataDict06.pdf
How many properties are worth $1,000,000 or more?

```{r}
fileurl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv"
download.file(fileurl, destfile = "./data/acs.csv")
list.files("./data")
acs<- read.csv("./data/acs.csv")
head(acs$VAL)

```

```{r}
library(data.table)
DT<- data.table(acs) ## create data.table version
DT[, .N, by=VAL==24] ## find count of above $1,000,000 (24)

```
Question 2
Use the data you loaded from Question 1. Consider the variable FES in the code book. Which of the "tidy data" principles does this variable violate? 
```{r}
head(acs$FES)
```
Question 3
Download the Excel spreadsheet on Natural Gas Aquisition Program here:
https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx
Read rows 18-23 and columns 7-15 into R and assign the result to a variable called:
dat
What is the value of:
sum(dat$Zip*dat$Ext,na.rm=T)

```{r}
library(openxlsx)
filexlsx<- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx"
download.file(filexlsx, destfile = "./data/NGAP.xlsx", mode = "wb")
rowIndex<- 18:23
colIndex<- 7:15
dat<- read.xlsx("./data/NGAP.xlsx", sheet=1, rows=rowIndex, cols = colIndex)
sum(dat$Zip*dat$Ext, na.rm = TRUE)
```
Question 4
Read the XML data on Baltimore restaurants from here:
https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml 
How many restaurants have zipcode 21231? 

```{r}
library(XML)
library(RCurl)
library(dplyr)

filexml<- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml"

xData<- getURL(filexml)
doc<- xmlParse(xData)
rootNode<-xmlRoot(doc)

zips<- xpathSApply(rootNode, "//zipcode", xmlValue)
zips_dt <- data.frame(zips, row.names = NULL)

count(zips_dt, zips==21231)

```


Question 5
The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here: 
https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv
using the fread() command load the data into an R object

DT


The following are ways to calculate the average value of the variable

pwgtp15


broken down by sex. Using the data.table package, which will deliver the fastest user time? 

```{r}
library(data.table)
download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv", destfile = "ACS.csv")
DT <- fread("ACS.csv", sep = ",")

library(microbenchmark)
mbm =microbenchmark(v3 =sapply(split(DT$pwgtp15,DT$SEX), mean),
                    v6 = DT[,mean(pwgtp15), by=SEX],
                    v7 = tapply(DT$pwgtp15, DT$SEX, mean),
                    v8 = mean(DT$pwgtp15, by=DT$sex),
                    times = 100)
mbm
```

